\propertitle

### 2020-03-17 replies1_ncomp.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2020-03-17T02:34:29+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourtrue% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimfalse
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\firstdraft}{16 March 2020}
\newcommand*{\firstpublished}{16 March 2020}
\newcommand*{\updated}{\ifarxiv***\else\today\fi}
\newcommand*{\propertitle}{Sketch of replies to N. Comp. reviews%\\{\large ***}%
}% title uses LARGE; set Large for smaller
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{}
\newcommand*{\pdfauthor}{}
\newcommand*{\headauthor}{}
\newcommand*{\reporthead}{}%\ifarxiv\else Open Science Framework \href{https://doi.org/10.31219/osf.io/***}{\textsc{doi}:10.31219/osf.io/***}\fi}% Report number

@@

There are many differing, fragmented views on the questions of comparison,
complexity, nesting, and \enquote{penalization} of models. Our view is
close to that expressed in several works, studies, and commentaries
\footcites[\eg][]{good1950,good1985,kadaneetal1980b,jonesetal1986,chatfield1995,copasetal1995,draper1995,spiegelhalteretal1995,raftery1995,gelmanetal1995,mackay1995_r2003,draperetal1996,hoetingetal1999,clydeetal1999,browneetal2006},
and well-explained in MacKay \citey{mackay1992}. According to this view,
which we summarize below, the log-evidence automatically takes care of
model complexity. This view hinges on a clear definition of what a
\enquote{model} is.

If by \enquote{model} we mean a family of probability distributions, \eg\
(apart from normalization)
\[\conds*{\exp\biggl[-\frac{(x-\mu)^{2}}{2\sigma^{2}}\biggr]\,\di x}{
    \mu\in\RR, \sigma \in \RR_{>0}}\;,\]
then model comparison is ill-defined. % Each distribution in the family
% assigns a different probability, and it is not clear which should be
% chosen or how they should be combined and why.
It may happen that the optimal distribution in family $\mathcal{F}_{1}$
assigns more probability to the observed data than the optimal distribution
in family $\mathcal{F}_{2}$, and yet $\mathcal{F}_{1}$ assigns \enquote{on
  average} lower probabilities to the data than $\mathcal{F}_{2}$. It is
not clear how the two families should be compared in this case, or what
$\p(D \| \mathcal{F}_{i})$ is. A hypothesis is ill-defined, or at least
useless, if it does not allow us to assign a probability to the data. Such
a probability can be obtained if we specify a pre-data probability
distribution over the distributions in the family, \eg\
$\pf(\mu,\sigma \| I)\,\di\mu\,\di\sigma$ in the example above.
\enquote{Model} must be therefore redefined as a family of distributions
\emph{and} a pre-data distribution over such family
\citep{dawid1982,dawid1993}. This redefinition also turns out to be
equivalent, under exchangeability, to the specification of a single
predictive distribution, that is, a joint probability for any number of
samples
\citep[\chap~4]{bernardoetal1994_r2000}{fortinietal2000,ressel1983_r1985,lauritzen1984}.
This redefinition has several consequences:

@@

As stated on p.~8, the interpretation is important because it leads to
numerically different results in first- and higher-order approximations.
And such approximations may be necessary in the precise calculation of the
evidence, as explained in the reply to the previous point. Appendix~C
explains where and why the numerical differences appear. Also, it is
important to know whether we are calculating the frequency of past results,
or the probability for a new result, or the most probable frequency of
future results. These three quantities can be numerically very different
when the ratio $\frac{\text{\# samples}}{\text{data-space dimension}}$ is
high, and they are to be used in different ways. Preliminary calculations
from the full Bayesian analysis show that%
\setlength{\intextsep}{-1ex}% with wrapfigure
\setlength{\columnsep}{0ex}% with wrapfigure
\begin{wrapfigure}{r}{0pt} % with wrapfigure
\centering\includegraphics[width=0.5\linewidth]{example_fullbayesian.pdf}
%\caption{caption}\label{fig:comparison_a5}
\end{wrapfigure}% exp_family_maxent.nb
the most probable frequency distribution across recorded bins (item i on
p.~8) and the belief distribution over the total activity at any recorded
bin (item ii on p.~8) are visibly different. See figure on the right: the
first is the red dashed red curve, the second the solid green line.

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2020-03-17T12:01:54+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourtrue% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimfalse
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\firstdraft}{16 March 2020}
\newcommand*{\firstpublished}{16 March 2020}
\newcommand*{\updated}{\ifarxiv***\else\today\fi}
\newcommand*{\propertitle}{Sketch of replies to N. Comp. reviews%\\{\large ***}%
}% title uses LARGE; set Large for smaller
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{}
\newcommand*{\pdfauthor}{}
\newcommand*{\headauthor}{}
\newcommand*{\reporthead}{}%\ifarxiv\else Open Science Framework \href{https://doi.org/10.31219/osf.io/***}{\textsc{doi}:10.31219/osf.io/***}\fi}% Report number

@@

There are many differing, fragmented views on the questions of comparison,
complexity, nesting, and \enquote{penalization} of models. Our view is
close to that expressed in several works, studies, and commentaries
\footcites[\eg][]{good1950,good1985,kadaneetal1980b,dawid1982,dawid1993,jonesetal1986,chatfield1995,copasetal1995,draper1995,spiegelhalteretal1995,raftery1995,gelmanetal1995,mackay1995_r2003,draperetal1996,hoetingetal1999,clydeetal1999,mccullagh2002,browneetal2006},
and well-explained in MacKay \citey{mackay1992}. According to this view,
which we summarize below, the log-evidence automatically takes care of
model complexity. This view hinges on a clear definition of what a
\enquote{model} is.

If by \enquote{model} we mean a family of probability distributions, for
example (apart from normalization)
\[\conds*{\exp\biggl[-\frac{(x-\mu)^{2}}{2\sigma^{2}}\biggr]\,\di x}{
    \mu\in\RR, \sigma \in \RR_{>0}}\;,\]
then model comparison is ill-defined. % Each distribution in the family
% assigns a different probability, and it is not clear which should be
% chosen or how they should be combined and why.
It may happen that the optimal distribution in family $\mathcal{F}_{1}$
assigns more probability to the observed data than the optimal distribution
in family $\mathcal{F}_{2}$, and yet $\mathcal{F}_{1}$ assigns \enquote{on
  average} lower probabilities to the data than $\mathcal{F}_{2}$. It is
not clear how the two families should be compared in this case, or what
$\p(D \| \mathcal{F}_{i})$ is. A hypothesis is ill-defined, or at least
useless, if it does not allow us to assign a probability to the data. Such
a probability can be obtained if we specify a pre-data probability
distribution over the distributions in the family, \eg\
$\pf(\mu,\sigma \| I)\,\di\mu\,\di\sigma$ in the example above.
\enquote{Model} must be therefore redefined as a family of distributions
\emph{and} a pre-data distribution over such family
\citep{dawid1982,dawid1993}. This redefinition also turns out to be
equivalent, under exchangeability, to the specification of a single
predictive distribution, that is, a joint probability for any number of
data samples. Such a predictive distribution automatically determines a
family of parametric distributions and a distribution over such family
\citep[\chap~4]{bernardoetal1994_r2000}{fortinietal2000,ressel1983_r1985,lauritzen1984}.
This redefinition has several consequences:

@@

As stated on p.~8, the interpretation is important because it leads to
numerically different results in first- and higher-order approximations.
And such approximations may be necessary in the precise calculation of the
evidence, as explained in the reply to the previous point. Appendix~C
explains where and why the numerical differences appear. Also, it is
important to know whether we are calculating the frequency of past results,
or the probability for a new result, or the most probable frequency of
future results. These three quantities can be numerically very different
when the ratio $\frac{\text{\# samples}}{\text{data-space dimension}}$ is
high, and they are to be used in different ways. Preliminary calculations
from the full Bayesian analysis show that%
\setlength{\intextsep}{-1ex}% with wrapfigure
\setlength{\columnsep}{0ex}% with wrapfigure
\begin{wrapfigure}{r}{0pt} % with wrapfigure
\centering\includegraphics[width=0.5\linewidth]{example_fullbayesian.pdf}
%\caption{caption}\label{fig:comparison_a5}
\end{wrapfigure}% exp_family_maxent.nb
the most probable frequency distribution across recorded bins (item i on
p.~8) and the belief distribution over the total activity at any recorded
bin (item ii on p.~8) are visibly different. See figure on the right: item
(i) is the red dashed red curve, item (ii) the solid green line.
